Milestone 2: Feature Selection - Nearest Neighbors, Mahalanobis

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
NN Malahanobis feature selection

```{r fs1_int, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                      replace=TRUE, distance = 'mahalanobis')
}
save.image(results_file_path)
print(res_fs1)
```

>>>>

```{r fs1_int, error=TRUE}
res_fs1_int <- list()
for (bt in names(bts)){
  res_fs1_int[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                      replace=TRUE, distance = 'mahalanobis')
}
save.image(results_file_path)
print(res_fs1_int)
```
